\documentclass[twocolumn,10pt]{article}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{geometry}
\geometry{a4paper, margin=.9in}
\usepackage{hyperref}
\usepackage{titling}
\usepackage{tcolorbox}
\usepackage{epigraph}

% Customize epigraph
\setlength{\epigraphwidth}{0.95\textwidth} % Adjust epigraph width
\renewcommand{\textflush}{flushleft}     % Align quote to the left
\renewcommand{\sourceflush}{flushright}  % Align author to the right
\renewcommand{\epigraphsize}{\itshape} % Font size and style for quote


\title{What is a UOR Machine?}
\author{Mr.\ Lambaiso}
\date{\today}

\begin{document}

\twocolumn[
\maketitle
\begin{center}
\epigraph{Truth is ever to be found in simplicity, and not in the multiplicity and confusion of things.}{--- Isaac Newton}
 
\end{center}
\vspace{10pt}
]

\section*{An Abundance Machine}
Simply put, a UOR machine is a computer.

At the core, all computers require three [3] primary resources;
two parts and one component.
These three resources are the 1. CPU (logic-compute), 2. memory (storage) \& 3. bus (transport).
The CPU and memory are the non-relational parts.
The bus is the real-world, physical circuitry that connects the CPU to the memory.
The bus is the resource that ``connects'' the other two resources;
the component is the relationship between parts.
It is the configuring of these resources that the UOR machine computes.

Together these three resources allow for the creation of the runtime environment we are all familiar with.
These resources co-exist \& are co-ordinated on the Internet.
And exist in \textbf{abundance}.
Information or a service is simply a configuration of the primary resources to create (or allow) that information to be displayed or service to be rendered.
The Internet creates, and continues to create in real-time, a seemingly infinite number of these configurations to access and consume these resources.

The UOR machine is a re-configuration of the Internet, or a better configuration and use of the primary resources.
By reconfiguring the access and usage of the resources, in a real-time environement, it allows for a universal computer to abstract the physical dependencies required for a computer.
This exploitation abstracts the three primary resources for any computer to operate.

Current cloud platforms and modern operating systems are so well \textit{accepted} as computing standards, it is possible to abstract them away.
This is what the UOR machine does, by assuming \& trusting that these resources are readily available, always,  the UOR machine provides \textit{access} to all data and services on the Internet.
Creating a novel, powerful system to re-configure the Internet to the desires and intentions of a user.

This re-configuration of the co-ordination of the parts and components of a computer, allow for a more free and open use of the Internet.
Each UOR machine abstracts out the physical resources by simply assuming they will be there when it needs it.
This assumption is true.
Modern cloud networks and the stability of many operating systems allow for the access and use of any resource, anytime.
The UOR machine exploits this and re-focuses the user to ``see'' the Internet simply as a collection of all the data and services on the Internet.

This approach to the Internet creates a novel and simple interface with the Internet.
Now any user can perceive the data \& services, or \textit{function}, found on the Internet in their most simple and single \textit{form}.
A bank account, purchase a airplane ticket, find a movie, an entire cloud service like AWS, program a quantum computer, your personal website, anything desired by the user.
Each unique, simple function is encapsulated, or formed, by the UOR machine in a way that creates a tailored, runtime environment for YOU.
Any desire or intention of a user of the Internet will be able to re-configure the Internet to the user's will.
A bold statement indeed!
Anything desired\ldots only constrained by the limits of the entire Internet.

What does a user do if they can access and use any resource and data on the Internet?
That is well beyond my vision, because each UOR machine and it's user determine that;
the desired runtime environment, in real-time, using the UOR machine.

So, what is a UOR machine?
It is a computer that allows the user to interact with any service or data desired, in a way that delievers exactly what the user wants.
Due to the \textbf{abundance} of data \& services available on the Internet, the possibilities are infinite.

In danger of over-simplification, the UOR machine is a container for the Internet's data \& services.
It is ``THE'' container.
The container that allows the user to re-create their Internet experience beyond what is currently available.

I can't wait to see what \textbf{YOU} create with your UOR machine!
\end{document}
